---
title: "Bass Model"
author: "Hrag Soussani"
date: "2024-02-25"
output: pdf_document
---

I choose Amazon Echo Speaker as the past look-alike Innovation of Sonos Era 300 Speaker.

My justification is as follows:

The Echo was a sensation when it arrived in 2014, with its pioneering artificial intelligence voice-controlled speaker technology that made it the ultimate cool device. Before Sonos launched their speaker in 2017 society had already got used to talking to gadgets, which meant that not having voice control was not an option for Sonos. It is likely that Sonos watched the Echo very closely and realized there was a growing need for voice-controlled assistants, subsequently directly incorporating this feature into their Era 300 speakers. 

Sonos probably felt compelled to venture into the world of voice-controlled speakers because of the wide popularity of the Echo and also because they are known for making top-notch sound systems. The success recorded by the Echo has brought out a natural desire among people to converse with their devices, therefore prompting Sonos to give similar experience but with even more superior audio quality as usual. This enabled Sonos cash on what Echo had already done and make its system better like one improving an existing recipe while adding his/her own spices. 


About the Data Time Series:

I chose this data as a perfect fit for estimating the bass model parameters and it contains a long range of years (2013-2023)

```{r warning=FALSE}
library(ggplot2)
echo_data <- read.csv('Echo_Sales.csv')
echo_data

ggplot(echo_data, aes(Year, Sales)) + geom_bar(stat = 'identity')


```
``` {r}
library(diffusion)
diff_m = diffusion(echo_data$Sales)
p = round(diff_m$w,4)[1]
q = round(diff_m$w,4)[2]
m = round(diff_m$w,4)[3]
diff_m
```


``` {r}
t <- 1:length(echo_data$Year)
bass.f <- function(t,p,q) {
  ((p + q) ^ 2 / p) * exp(-(p + q) * t) / (1 + (q / p) * exp(-(p + q) * t)) ^ 2
}

bass.F <- function(t,p,q) {
  (1 - exp(-(p + q) * t)) / (1 + (q / p) * exp(-(p + q) * t))
}

```

``` {r}

ggplot(echo_data, aes(t)) +
  stat_function(fun = bass.F, args = c(p, q))

ggplot(echo_data, aes(t)) +
  stat_function(fun = bass.f, args = c(p, q))



```
``` {r}
echo_data$sonos_predicted_sales = bass.f(t, p, q) * m
ggplot(data = echo_data, aes(Year, Sales)) +
  geom_bar(stat = 'identity') +
  geom_point(aes(Year, sonos_predicted_sales), color = 'red')

```
``` {r}
sum(echo_data$Sales)
```

Estimating the market potential of the Sonos Era 300 Speaker using Fermi’s logic:

Let's say that there are 8 billion people in the world. 40% prefer to have speakers at their houses. However, considering the fact that there are wide variety of options that some prefer budget speakers, that 40% drops down to 25%. Now there are people that would like to have the option of the voice assitant, hence 25% goes down to 10%, now some don't prefer wired speakers (not battery based), so it will be 3%. So the final count comes to 240million tops.


Data: https://www.statista.com/statistics/1022701/worldwide-amazon-echo-unit-shipment/
